A Horrocks-type theorem for even orthogonal $K_2$

### 2020-09-08 dl-paper.tex
Purge most of the scaleboxes

\newline \scalebox{.88}{\begin{minipage}{1.13\linewidth} \begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
 = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip

@@

\newline \scalebox{.86}{\begin{minipage}{1.16\linewidth}\begin{align*} \nonumber

@@

= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*} \end{minipage}} \vskip \belowdisplayshortskip

@@

\newline \scalebox{.84}{\begin{minipage}{1.17\linewidth}\begin{align*}

@@

= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2)  &\ \text{by~\eqref{Chevalley-CCF1}}. \qedhere \end{align*} \end{minipage}} \vskip \belowdisplayshortskip

@@

 Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows: 
\newline\scalebox{0.96}{\begin{minipage}{1.04\linewidth}
 \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]\end{minipage}}\vskip \belowdisplayshortskip
 It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$. Thus, we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
 which implies the assertion. \qedhere \end{proof}

@@

\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\cref{Crels}\ref{C4} we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. The assertion of the corollary now easily follows from the irreducibility of $\Phi$. \end{proof}

@@

Whenever the coefficient $\xi$ of a Steinberg generator $g = x_\alpha(\xi)$ of $\St(\Phi, B)$ is a homogeneous element of $B$, i.\,e. $\xi \in B_d$ for some $d \in \mathbb{Z}$,
 we call the corresponding generator $g$ {\it homogeneous of degree $d$}.
We denote by $\St^h(\Phi, B)$ the group given by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations between them
(below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
\begin{align}
&\,\,x_{\alpha}(a)\cdot x_{\alpha}(a') =  x_{\alpha}(a+a'),                        & \tag{R$1_d$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),   & \alpha + \beta \in \Phi,\ \tag{R$2_{d,e}$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha \perp \beta.\ \tag{R$3^\bot_{d,e}$}
\end{align}
\begin{rem}
Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they follow from~$\text{R2}_{e,0}$, \eqref{eq:H1iii} and $\text{R3}_{d,e}^\angle$. Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we obtain that 
\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
\[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1. \]\end{minipage}}
\end{rem}

@@

\item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
\newline\scalebox{0.94}{\begin{minipage}{1.06\linewidth}
\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = \hspace{4cm} \\ = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
 = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
 = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
 = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}\end{minipage}}\vskip \belowdisplayshortskip
where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
\end{enumerate}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
\[S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\]
\end{lemma} \begin{proof} Suppose $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
\newline\scalebox{0.82}{\begin{minipage}{1.21\linewidth}
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1 x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}\end{minipage}}
\end{proof}

\begin{lemma} \label{lem:Tulenbaev-formula} 
One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}
 \begin{align} 
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) &\text{ by~\eqref{eq:conj-h-x}} \label{eq:Tf-comp} \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) &\text{ by~\eqref{eq:dennis-stein}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) &\text{ by~\eqref{eq:conj-h-x}, \eqref{eq:conj-h-h}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right)&\text{ by~\eqref{eq:steinberg}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}. \nonumber \end{align}\end{minipage}}
The assertion of the lemma now follows from the following computation:
\newline\scalebox{0.85}{\begin{minipage}{1.15\linewidth}\begin{align*}
 S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*}\end{minipage}}  \end{proof}

>>>>

\begin{align*} \nonumber [c_{\beta}(s, t),\ x_{\alpha}(\xi)] = [x_{\beta}(s),\ x_{-\beta}(t)] \cdot [x_{-\beta}(t),\ x_{\beta}(s)\cdot x_{\alpha + \beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{Cdef}, \eqref{Chevalley-CCF1}, \eqref{Chevalley-CCF2}} \\
 = {}^{x_\beta(s)}\![x_{-\beta}(t),\ x_{\alpha+\beta}(N_{\alpha, \beta} \cdot s\xi)] &\text{ by~\eqref{eq:H1ii-2}} \\ = x_{\alpha}(- st\xi) \cdot x_{\alpha+\beta}(N_{\alpha,\beta} \cdot s^2t\xi) &\text{ by~\eqref{Chevalley-CCF1}.} \end{align*}

@@

\begin{align*} \nonumber

@@

= x_{\alpha}(st\xi) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot st^2\xi)^{x_\beta(-s)} = x_{\alpha}(st\xi + s^2t^2 \xi) \cdot x_{\alpha-\beta}(N_{-\alpha,\beta}\cdot st^2\xi) & \text{ by~\eqref{Chevalley-CCF1}.} \end{align*}

@@

\begin{align*}

@@

= [x_{\beta}(st),\ x_{-\beta}(\xi)] ^ {x_{\alpha+\beta}(-s) x_{-\alpha}(\epsilon t)} \cdot c_{\alpha}(\epsilon s\xi, -\epsilon t)^{-1} \cdot x_{-\beta}(-st\xi^2)  &\ \text{by~\eqref{Chevalley-CCF1}}. \qedhere \end{align*}

@@

 Now each factor $z_{\alpha_i}(f_i(0), \xi_i(X))$ can be written as follows:

 \[z_{\alpha_i}(f_i(0), \xi_i(0))^{x_{-\alpha_i}(X\xi'_i(X))} = [x_{-\alpha_i}(-X\xi'_i(X)),\ z_{\alpha_i}(f_i(0), \xi_i(0))] \cdot z_{\alpha_i}(f_i(0), \xi_i(0)).\]
 It follows from the formula $[g,\ h]^{h_1} = [h_1^{-1},\ g][g,\ h_1^{-1}h]$ that the subgroup \[C_0 := \left[\St(\Phi, XA[X]),\ \overline{\St}(\Phi, A, M)\right]\] is normalized by $\overline{\St}(\Phi, A, M)$. Thus, we conclude that $g_1(X)$ is congruent to $\prod_i z_{\alpha_i}(f_i(0), \xi_i(0)) = g(0) = 1$ modulo $C_0$,
 which implies the assertion. \qedhere \end{proof}

@@

\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into~\cref{Crels}\ref{C4} we obtain that modulo the subgroup
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. The assertion of the corollary now easily follows from the irreducibility of $\Phi$. \end{proof}

@@

Whenever the coefficient $\xi$ of a Steinberg generator $g = x_\alpha(\xi)$ of $\St(\Phi, B)$ is a homogeneous element of $B$, i.\,e. $\xi \in B_d$ for some $d \in \mathbb{Z}$,
 we call the corresponding generator $g$ {\it homogeneous of degree $d$}.
We denote by $\St^h(\Phi, B)$ the group given by the set of all homogeneous Steinberg generators modulo the following set of Steinberg relations between them
(below $a, a' \in B_d$, $b\in R_e$ and $d,e \in \mathbb{Z}$): 
\begin{align}
&\,\,x_{\alpha}(a)\cdot x_{\alpha}(a') =  x_{\alpha}(a+a'),                        & \tag{R$1_d$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= x_{\alpha+\beta}(N_{\alpha, \beta} \cdot ab),   & \alpha + \beta \in \Phi,\ \tag{R$2_{d,e}$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha - \beta \in \Phi,\ \tag{R$3^\angle_{d,e}$} \\
&\,[x_{\alpha}(a),\,x_{\beta}(b)]= 1,                                              & \alpha \perp \beta.\ \tag{R$3^\bot_{d,e}$}
\end{align}
\begin{rem}
Notice that in the above presentation we omitted the relations $[x_\alpha(a), x_\alpha(b)] = 1$ but it easy to see that they follow from~$\text{R2}_{e,0}$, \eqref{eq:H1iii} and $\text{R3}_{d,e}^\angle$. Indeed, after choosing some root $\beta\in \Phi$ such that $\alpha+\beta\in\Phi$ and setting $\epsilon = N_{\alpha+\beta,-\beta}$ we obtain that 
\[ [x_\alpha(a),\ x_\alpha(b)] = [x_\alpha(a),\ [x_{\alpha+\beta}(b),\ x_{-\beta}(\epsilon)]] = [[x_\alpha(a),\ x_{\alpha+\beta}(b)],\ {}^{x_{\alpha+\beta}(b)}\!x_{-\beta}(\epsilon)] = 1. \] \end{rem}

@@

\item In the case $d \leq 0 \leq e \leq n$ the relation $R$ is a consequence of some relation of type $\text{R3}^\bot_{1,d+e-1}$:
\begin{align*} [x_\alpha(at^d), x_{\gamma}(bt^{e})] = \hspace{4cm} \\ = [x_\alpha(at^d), [x_{\beta+\gamma}(b t^{e-1}), x_{-\beta}(-\epsilon_1 t)]] & \text{ by~$\text{R2}_{e-1,1}$ } \\
 = [[x_\alpha(at^d), x_{\beta+\gamma}(bt^{e-1})], {}^{x_{\beta+\gamma}(bt^{e-1})}\!x_{-\beta}(-\epsilon_1 t)] & \text{ by \eqref{eq:H1iii} and $\text{R3}^\angle_{d,1}$ } \\
 = {}^{x_{\beta+\gamma}(bt^{e-1})}\![x_{\alpha+\beta+\gamma}(\epsilon_2abt^{d+e-1}), x_{-\beta}(-\epsilon_1 t)] & \text{ by $\text{R2}_{d,e-1}$ and $\text{R3}^\angle_{e-1,d+e-1}$  } \\
 = 1 & \text{ by $\text{R3}^\bot_{1,d+e-1}$,} \end{align*}
where $\epsilon_1 = N_{\beta,\gamma}$, $\epsilon_2 = N_{\alpha,\beta+\gamma}$.
\end{enumerate}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
\[S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\]
\end{lemma} \begin{proof} Suppose $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:

\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1 x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}

\begin{lemma} \label{lem:Tulenbaev-formula} 
One has $S_\alpha(a, x_{-\alpha}(mX)) = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am).$
\end{lemma}
\begin{proof} Since $\Phi$ is nonsymplectic, we can choose $\gamma \in \Phi$ such that $\langle \alpha, \gamma \rangle = -1$. Direct computation shows that
 \begin{align} 
 x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) = {}^{h_\gamma(X)}(x_\alpha(a) \cdot x_{-\alpha}(m)) &\text{ by~\eqref{eq:conj-h-x}} \label{eq:Tf-comp} \\
 = {}^{h_\gamma(X)}\left( x_{-\alpha}\left(\tfrac{m}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_\alpha\left(\tfrac{a}{1+am}\right) \right) &\text{ by~\eqref{eq:dennis-stein}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(X^{-1}(1+am))\cdot h_\alpha^{-1}\left(X^{-1}\right) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) &\text{ by~\eqref{eq:conj-h-x}, \eqref{eq:conj-h-h}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot \{X^{-1}, 1+am\} \cdot h_\alpha(1+am)\cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right)&\text{ by~\eqref{eq:steinberg}} \nonumber \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\tfrac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\}&\text{ by~\eqref{eq:symbol-properties}, \eqref{eq:symbol-inverse}}. \nonumber \end{align}
The assertion of the lemma now follows from the following computation:
\begin{align*}
 S_\alpha(a, x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\} &\text{ by~\eqref{eq:S-def}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot \{1+am, X\} \cdot \{X, 1+ am\}&\text{ by~\eqref{eq:Tf-comp}} \\
 = x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m\rangle_\alpha \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:symbol-properties}}. \qedhere\end{align*} \end{proof}

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ one has $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am}).$
%, moreover, \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]
\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Direct computation shows that
\begin{align*}
 S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am)&\text{ by~\cref{lem:Smult}} \\\
 = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle &\text{ by~\cref{lem:Tulenbaev-formula}.}
\end{align*}
By \cref{P0_conj} and \cref{rem:DS} the subgroup $P_\alpha(0)$ contains $S_\alpha(a, g_0)$ and the symbol $\langle a, m \rangle$. Thus, the expression in the right-hand side of the above formula lies in $P_\alpha\left(\tfrac{m}{1+am}\right)$. 
\end{proof}
\begin{comment}
\begin{corollary}\label{cor:additivity} For $a, b \in A$ and $g \in P_\alpha(m)$ one has
 \[S_\alpha(a + b, g) = S_\alpha\left(b, S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am)\right) \cdot h_\alpha(1+am).\]
\end{corollary}
\begin{proof}
The assertion immediately follows from the above corollary:
 \begin{align*}
  S_\alpha\left(b, S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am)\right) \cdot h_\alpha(1+am) &\text{ by~\eqref{eq:S-def}} \\
  = x_\alpha(bX^{-1}) \cdot S_\alpha(a, g) \cdot h_\alpha^{-1}(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1+\tfrac{bm}{1+am}}\right) \cdot \{X, 1+\tfrac{bm}{1+am}\} \cdot h_\alpha(1+am)&\text{ by~\eqref{eq:conj-h-x}} \\
  = x_\alpha(bX^{-1}) \cdot S_\alpha(a, g) \cdot x_\alpha\left(\tfrac{-bX^{-1}}{(1+am)(1+am+bm)}\right) \cdot \left\{X, 1+\tfrac{bm}{1+am} \right\}&\text{ by~\eqref{eq:S-def}}\\
  = x_\alpha((a+b)X^{-1}) \cdot h \cdot x_\alpha\left(- \tfrac{aX^{-1}(1+am+bm) + bX^{-1}}{(1+am)(1+am+bm)} \right) \cdot \{ X, 1+(a+b)m \} = S_\alpha(a+b, g) &\text{ by~\eqref{eq:S-def}.} \end{align*}
\end{proof}
\end{comment}
\begin{lemma} \label{SR:sharp} For $g \in j_+(K(A[X], M[X])) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ one has \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$. By~\cref{K-a-b-P-b} the element $g_1 = S_\alpha(a, g_0) $ lies in $P_\beta(0)$. Since $x_{-\beta}(m'X) \in P_\alpha(0)$ we get that
\newline\scalebox{.98}{\begin{minipage}{1.02\linewidth}\begin{align*}
  S_\alpha(a, g) = g_1 \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) & \text{ by~\cref{lem:Smult}} \\ 
  = g_1 \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) & \text{ by~\cref{lem:Tulenbaev-formula},\eqref{Chevalley-CCF1}} \\
  = g_1 \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am) & \text{ by~\eqref{eq:conj-h-x}}.
\end{align*}\end{minipage}} \vskip \belowdisplayshortskip
The required assertion now follows from~\cref{rem:palpha}.
\end{proof}
